### 2023-04-18 reachable-resilience.tex
up

\begin{proof}
Consider Reset $d$-VASS
with $\Safe$ % where  $ \textbf{0} = 0^d \in \mathbb{N}^d$ 
	containing only the
		configurations of the form $Q \times \{ \textbf{0} \}$
	where $\textbf{0} = \min(\mathbb{N}^d)$ %$0$ 
% \alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$, 
it follows
{\sc State-resilience} 
% \alain{écris toujours pareil les expressions choisies comme state-resilience}
is equivalent 
to the problem of whether 
% $0$  can be visited infinitely often. 
it is possible to visit infinitely often configurations with every vector having its value equal to $0$.
\alain{incompréhensible, explique}
Indeed, from such a configuration, then the next step is either also such a configuration, either it is in $\Bad$, in which case, we know it is possible to reach such a configuration again. Hence we construct a sequence 
$(q_i ({\textbf{v}_{i}}) )_{i\in\N}$ 
such that for all $i\in\N$ 
$\exists j \in \N$, $j>i$, s.t. ${\textbf{v}_j} = \textbf{0}$.
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}

>>>>

\begin{proof}
Consider Reset $d$-VASS
with $\Safe$ % where  $ \textbf{0} = 0^d \in \mathbb{N}^d$ 
	containing only the
		configurations in $Q \times \{ \textbf{0} \}$
	where $\textbf{0} = \min(\mathbb{N}^d)$ %$0$ 
% \alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$.
It follows in this case that
{\sc State-resilience} 
% \alain{écris toujours pareil les expressions choisies comme state-resilience}
is equivalent 
to the problem of whether 
% $0$  can be visited infinitely often. 
it is possible to visit infinitely often configurations with every vector having its value equal to $0$.
\alain{incompréhensible, explique}
Indeed, from such a configuration, then the next step is either also such a configuration, either it is in $\Bad$, in which case, we know it is possible to reach such a configuration again. Hence we construct a sequence 
$(q_i ({\textbf{v}_{i}}) )_{i\in\N}$ 
such that for all $i\in\N$ 
$\exists j \in \N$, $j>i$, s.t. ${\textbf{v}_j} = \textbf{0}$.
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}
